\documentclass[../professional-cv.tex]{subfiles}
\begin{document}
\begin{rSection}{Work Experience}
	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	\begin{rWorkSection}
		{\href{https://yektanet.com/}{Yektanet}}
		{Tehran, Iran}

		\vspace{-1em}
		{\em Software Engineer at Data Platform Team} \hfill {\em Nov. 2023 - Present} \hspace{10pt}
		\normalfont
		\begin{list}{$\cdot$}{\leftmargin=10pt\normalfont \rightmargin=20pt}
			\itemsep -0.5em
			\item Took inititative in the process of revamping the team's monitoring/alerting mechanism, developing various new dashboards and alert rules with on-call support.
			\item Administered a 10 Node hadooop cluster, with high availability settings using Ansible deployed on a baremetal cluster.
			\item Administered a 16 Node K8s cluster for the data platform team, with various production services on it (Airflow, Spark, Kafka Connectors).
			\item Utilized, improved and developed various helm charts for internal toolings and production services, e.g. Hue HDFS Browser, JupyterHub.
			\item Adminstered a K8s based spark development workflow utilizing JupyterHub, SparkOperator, Airflow which enabled data teams to rapidly prototype and create data.
			\item Introduced a set of MLOps toolings to define the standard ml workflow in Yektanet using Ray, Spark, MLFlow on top of k8s.
			\item Developed a new set of kafka connectors that synced data from kafka to HDFS, and designed a local workflow to test these before deployment.
			\item Developed a new set of airflow dags to ingest data from various sources to HDFS via IceBerg, and sync from IceBerg to clickhouse.
			\item Adminstered a 2 node clickhouse cluster setup on K8s, developing monitroing mechanism to track data ingestion from OLTP sources.
			\item Took initiative in the design and development process of a brand new service to handle 5x rps with 0.1x resources using Go to replace an old bottleneck python service.
		\end{list}
	\end{rWorkSection}

	\begin{rWorkSection}
		{\href{https://aimedic.co/}{AIMedic}}
		{Tehran, Iran}

		\vspace{-1em}
		{\em Platform Team Lead} \hfill {\em Sep. 2021 - Nov 2023} \hspace{10pt}
		\normalfont
		\begin{list}{$\cdot$}{\leftmargin=10pt\normalfont \rightmargin=20pt}
			\itemsep -0.5em
			\item Led the team in the process of developing an MVP of an MLOps as a service platform. Stack: Prefect, gRPC, Flask, SQLAlchemy, Celery, Postgres, Redis, Minio, Ansible, Docker.
			\item Led the process of developing internal tools and plugins for ML pipelines, e.g. data registry, model registry and feature store solutions. Stack: Python, FastAPI, Docker, DVC, Metaflow, MLflow, Postgres, Minio.
			\item Defined and standardized development process and led the team to implement CI pipelines for all services using Gitlab CI and Harbor.
			\item Standardized the process of service monitoring by onboarding development teams to the Grafana, Loki, Prometheus stack, maintining the monitoring platforms and improving observability.
		% \end{list}
		% {\em ML Team Lead} \hfill {\em Aug. 2021 - Mar. 2022}
		% \normalfont
		% \begin{list}{$\cdot$}{\leftmargin=10pt\normalfont \rightmargin=20pt}
		% 	\itemsep -0.5em
			\item Led the team to develop ML solutions for arrhythmic ECG and epileptic EEG classification tasks. Stack: PyTorch, MNE, Pandas, HDF5.
		\end{list}
	\end{rWorkSection}

	\begin{rSubsection}
		{\href{https://hamsaa.ir}{Hamsaa}}
		{ \fmtdate{01}{2019} - \fmtdate{11}{2019} }
		{Software Engineer}
		{Tehran, Iran}
		\item Worked as a SWE on an inter-company social media solution. Stack: Java, Kotlin, Android, Git.
		\item Developed important features such as in-app video player, in-app file downloader and guided tour for on-boarding new users.

	\end{rSubsection}



	%----------------------------------------------------------------------------------------
\end{rSection}
\end{document}
